Title

### 2025-02-06 index.qmd
adding metros to rq2

```{r setup, echo=FALSE, results = 'asis'}
```{r, echo=FALSE, results='asis'}
library(tidyverse)
library(kableExtra)  # For collapse_rows() to work
library(tools)

@@

# 3) Subset of metros with RQ2 data (2 orders each)
rq2_metros <- c(
  "chicago", "philadelphia", "los angeles", 
  "orange county", "san diego", "bay area",
  "northern new jersey"
)

# We'll define a "metro_orders" list for those RQ2 metros:
metro_orders <- list(
  "chicago"             = c("487984", "488035_488053"),
  "philadelphia"        = c("448922", "448427_448440"),
  "northern_new_jersey" = c("448922", "448427_448440"),
  "los_angeles"         = c("448375", "448374_448420"),
  "orange_county"       = c("448375", "448374_448420"),
  "san_diego"           = c("448375", "448374_448420"),
  "bay_area"            = c("448375", "448374_448420")
)

@@

    # ---------------------------------------------
    # RQ2 Logic (row vs. col approach)
    # ---------------------------------------------
    } else if (rq == "rq2") {

@@

      # If a metro isn't in the list or no orders, skip
      if (is.null(orders_for_m)) next

@@

          } # end if row vs col

@@

>>>>

```{r setup, echo=FALSE, results = 'asis'}

library(tidyverse)
library(kableExtra)  # For collapse_rows() to work
library(tools)

@@

# 3) Subset of metros with RQ2 data (2 orders each)
rq2_metros <- c(
  "chicago", "philadelphia", "los angeles", 
  "orange county", "san diego", "bay area",
  "northern new jersey","long island",'detroit','dallas'
)

# We'll define a "metro_orders" list for those RQ2 metros:
metro_orders <- list(
  "chicago"             = c("487984", "488035_488053"),
  "philadelphia"        = c("448922", "448427_448440"),
  "northern_new_jersey" = c("448922", "448427_448440"),
  "long_island"         = c("448922", "448427_448440"),
  "detroit"             = c("448922", "448427_448440"),
  "dallas"              = c("448922", "448427_448440"),
  "los_angeles"         = c("448375", "448374_448420"),
  "orange_county"       = c("448375", "448374_448420"),
  "san_diego"           = c("448375", "448374_448420"),
  "bay_area"            = c("448375", "448374_448420")
)

@@

    # ---------------------------------------------
    # RQ2 Logic (row vs. col approach + race_by_firstgen)
    # ---------------------------------------------
    } else if (rq == "rq2") {

@@

      # If a metro isn't in the list or has no orders, skip
      if (is.null(orders_for_m)) next

@@

          } # end if (row vs col)

@@

      # -------------------------------------------
      # ADDITIONAL: race_by_firstgen for each order
      # -------------------------------------------
      # Like the column approach, one slide per order_id
      for (order_id in orders_for_m) {
        writeLines(str_c("### Research question ", rq_num))
        # Filenames look like:
        #   rq2_northern_new_jersey_order_448922_race_by_firstgen.png
        graph_type_rbf <- str_c("order_", order_id, "_race_by_firstgen")
        insert_figure(rq = rq, metro = m, graph_type = graph_type_rbf)
      }
